### 2017-04-02 paper/sections/Formalization.tex
more.
Added an example.

\subsection{Subtyping}
See Figure~\ref{fig:subtyping}.

@@

\subsection{Typing Rules}
See Figure~\ref{fig:typingrules}.

@@

\subsection{Small-step Semantics}
See Figure~\ref{fig:smallstep}.

@@

\subsection{Congruence}
See Figure~\ref{fig:congruence}.

@@

\subsubsection{\mtype}
$\mtype(m, C)$ algorithm:
\begin{itemize}
	\item If the result of $\mbody(m, C, A)$ is a unique method,\\
	$\method{I_0}{m}{I}{x}{J}{e_0}$,\\
	then $\mtype(m, C) = \overline{I} \to I_0$
	\item Else ($\Undefined$ or multiple methods returned), $\mtype(m, C) = \Error$
\end{itemize}

\subsubsection{\ext}
\ext(I,J) means interface $I$ (directly) extends $J$.

\subsubsection{\collectMethods}
\[ \collectMethods(I) = \left( \bigcup_{I_i \in \overline{I}} \methods(I_i) \right) \bigcup \methods(I) \]
\[ \methods(I) = \overline{M}, \text{where } IT(I) = \interface{I}{I}{M} \]

\subsubsection{\needed}

\subsubsection{\only}
$\only(m, I)$ is true iff inside $I$ there is only one (direct) methoed $m$ definition.

@@

>>>>

\subsection{Subtyping}
See Figure~\ref{fig:subtyping}. \haoyuan{TODO}

@@

\subsection{Typing Rules}
See Figure~\ref{fig:typingrules}. \haoyuan{TODO}

@@

\subsection{Small-step Semantics}
See Figure~\ref{fig:smallstep}. \haoyuan{TODO}

@@

\subsection{Congruence}
See Figure~\ref{fig:congruence}. \haoyuan{TODO}

@@

\subsubsection{\mtype}

\haoyuan{TODO. mtype(m, I) from mbody(I, I).}

\begin{comment}
\subsubsection{\collectMethods}
\[ \collectMethods(I) = \left( \bigcup_{I_i \in \overline{I}} \methods(I_i) \right) \bigcup \methods(I) \]
\[ \methods(I) = \overline{M}, \text{where } IT(I) = \interface{I}{I}{M} \]
\end{comment}

@@

\subsubsection{A Non-Trivial Example}

\[
\begin{array}{l}
\kwinterface \; A \; \kwextends \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; A \; \{\kwreturn \; \new A;\} \\
\} \\
\\
\kwinterface \; B \; \kwextends \; A \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new B;\} \\
\} \\
\\
\kwinterface \; C \; \kwextends \; A \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; C \; \{\kwreturn \; \new C;\} \\
\} \\
\\
\kwinterface \; D \; \kwextends \; B, \; C \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new D;\} \\
\} \\
\\
\kwinterface \; E \; \kwextends \; B \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new E;\} \\
\} \\
\\
\kwinterface \; F \; \kwextends \; D, \; E \; \{ \\
\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new F;\} \\
\; \; \; \; A \; n(B \; b) \; \kwoverride \; F \; \{\kwreturn \; b.m();\} \\
\} \\
\\
\new F.n(\new F)
\end{array}
\]

~\haoyuan{Unfortunately I think this example shows that it is hard to reuse
	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}

\haoyuan{We can use the $\kwsuper$ keyword to access the originally defined methods
	in super types, but we cannot access the old updating methods.}

\haoyuan{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}

Interfaces $A,B,C,D,E,F$ OK in type checking.

To type-check $\new F.n(\new F)$:
\begin{itemize}
	\item By (T-INVK), we need to calculate $\mtype(n, F)$.
	\item $\mtype(n, F) = B \to A$. And $\new F : B$.
	\item $\new F.n(\new F) : A$.
\end{itemize}

~

To compute \red{$\new F.n(\new F)$}:
\begin{itemize}
	\item By (C-RECEIVER), we compute \red{$\new F$}:
		\begin{itemize}
			\item By (C-STATICTYPE): \red{$<F> \new F$}.
		\end{itemize}
	\item By (C-ARGS), we compute \red{$\new F$}:
		\begin{itemize}
			\item By (C-STATICTYPE): \red{$<F> \new F$}.
		\end{itemize}
	\item Now we get \red{$(<F> \new F).n(<F> \new F)$}. By (S-INVK):
		\begin{itemize}
			\item Compute $\mbody(n, F, F) = \red{(B \; b, A \; b.m())}$.
			\item Replace \red{$b$} with \red{$<B> \new F$} in \red{$b.m()$}.
			\item Replace \red{$\kwthis$} with \red{$<F> \new F$} in \red{$b.m()$}.
		\end{itemize}
	\item Finally we get \red{$<A>((<B> \new F).m())$}.
	\item By (C-FREDUCE), we first compute \red{$(<B> \new F).m()$}:
		\begin{itemize}
			\item By (S-INVK), we compute \red{$\mbody(m, F, B)$}.
			\item In $\mbody$, we invoke \red{$\mostSpecific(m, F, B)$}.
			\item In $\mostSpecific$, \red{$set = \{B\}$, $\prune(set) = \{B\}$}.
			\item Back to $\mbody$, we invoke \red{$\mostSpecific_3(m, F, B)$}.
			\item In $\mostSpecific_3$, \red{$set = \{B,D,E,F\}$, $\prune(set) = \{F\}$}.
			\item Back to $\mbody$, we check \red{$F.m$} and return \red{$(-,A \; (\new F))$}.
			\item Back to (S-INVK).
			\item Replace \red{$\kwthis$} with \red{$<B> \new F$} in \red{$\new F$}.
			\item Finally we get \red{$<A> \new F$}.
		\end{itemize}
	\item Now we have \red{$<A>(<A> \new F)$}.
	\item By (C-ANNOREDUCE): \red{$<A> \new F$}.
\end{itemize}
